Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-20 manuscript/ERL_global_C_review.Rmd
small update

**(The following covers only the variables with age trends figures; there maybe a few more without much age data)**
With only # exceptions, C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests (Table 1, Figs. 6, S1-S15).
In this majority of cases, differences between tropical and boreal forests were always significant, with temperate forests intermediate and significantly different from one or both. 
Fluxes tended to be greater in temperate broadleaf than conifer forests, but the difference was never significant.
This pattern held for the following variables: $GPP$, $NPP$, $ANPP$, $ANPP_{woody}$, $ANPP_{stem}$, $ANPP_{foliage}$, $ANPP_{litterfall}$, $BNPP$, $BNPP_fine$, $R_{eco}$, $R_{root}$, $R_{soil}$, and $R_{het-soil}$.  
The most notable exception to this pattern was $NEP$, with no significant differences across biomes but with the largest average in temperate broadleaf forests, followed by temperate conifer, boreal, and tropical forests (Figs. 5,S1).
Another exception was for $BNPP_{root-coarse}$, where all records came from high-biomass forests in the US Pacific Northwest, resulting in high values for the temperate conifer biome and no significant differences across biomes (Fig. S10).  
Thus, C cycling rates generally decreased from tropical to temperate to boreal forests, with the important exception in the overall C balance ($NEP$).

@@

There were fewer distinct trends in C stocks across biomes (Figs. 7, S16-S26). 
Specifically, there were significant differences for only *#* of *#* variables: *LIST*. 
In all of these cases, temperate conifer forests were in the highest significance grouping, and boreal forests in the lowest. 
Tropical and temperate broadleaf forests fell in between--most commonly being significantly different from temperate conifer but not boreal forests.
... 
*(These differences are driven more by geographic distribution of sampling than by true differences.)*

@@

Closure of the C cycle budgets for mature forests (Figs. 2-5) is fairly good. 
However, SD's are often large, reflective of significant within-biome variation. This makes the standard for closure relatively loose.
Lack of closure, in the few instances where it occurs, is probably more reflective of differences in the representation of forest types (e.g., disproportionate representation of US Pacific NW for aboveground woody biomass relative to AGB; Fig. 4) than of methodological accuracy.
Thus, overall, a high degree of closure implies that ForC gives a consistent picture of C cycling within biomes. 
While these means are unlikely to be accurate representations of C cycling within any particular forest, they provide a useful baseline for comparison.

@@

>>>>

**(The following covers only the variables with age trends figures; there maybe a few more without much age data)**
With only # exceptions, C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests (Table 1, Figs. 6, S1-S15).
In this majority of cases, differences between tropical and boreal forests were always significant, with temperate forests intermediate and significantly different from one or both. 
Fluxes tended to be greater in temperate broadleaf than conifer forests, but the difference was never significant.
This pattern held for the following variables: $GPP$, $NPP$, $ANPP$, $ANPP_{woody}$, $ANPP_{stem}$, $ANPP_{foliage}$, $ANPP_{litterfall}$, $BNPP$, $BNPP_fine$, $R_{eco}$, $R_{root}$, $R_{soil}$, and $R_{het-soil}$.

The most notable exception to this pattern was $NEP$, with no significant differences across biomes but with the largest average in temperate broadleaf forests, followed by temperate conifer, boreal, and tropical forests (Figs. 5,S1).
Another exception was for $BNPP_{root-coarse}$, where all records came from high-biomass forests in the US Pacific Northwest, resulting in high values for the temperate conifer biome and no significant differences across biomes (Fig. S10).  
Thus, C cycling rates generally decreased from tropical to temperate to boreal forests, with the important exception in the overall C balance ($NEP$).

@@

There were fewer distinct trends in C stocks across biomes (Figs. 7, S16-S26). 
Specifically, there were significant differences for only *#* of *#* variables: *LIST*. 
In all of these cases, temperate conifer forests were in the highest significance grouping, and boreal forests in the lowest. 
Tropical and temperate broadleaf forests fell in between--most commonly being significantly different from temperate conifer but not boreal forests.
Once again, the high values for the temperate conifer biome were driven by the very high-biomass forests of the US Pacific Northwest, which are disproportionately represented in the current version of ForC. 
Thus, biome differences should be interpreted more as driven more by geographic distribution of sampling than by true differences.)*

@@

Closure of the C cycle budgets for mature forests (Figs. 2-5) is fairly good. 
However, SD's are often large, reflective of significant within-biome variation. This makes the standard for closure relatively loose.
Lack of closure, in the few instances where it occurs, is probably more reflective of differences in the representation of forest types (e.g., disproportionate representation of US Pacific NW for aboveground woody biomass relative to AGB; Fig. 4) than of methodological accuracy.
Thus, overall, a high degree of closure implies that ForC gives a consistent picture of C cycling within biomes. 
While these means are unlikely to be accurate representations of C cycling within any particular forest, they provide a useful baseline for comparison, always keeping in mind that sample means do not necessarily represent the true mean of the entire biome.

@@

Thus, biome differences should be interpreted more as driven more by geographic distribution of sampling than by true differences.
